Constant Error Tolerance Computational Fuzzy Extractors

### 2014-01-14 constantRate/ConstCompFuzzExt.tex
adding a lot on characterizing block sources

We now describe a set of high entropy sources appropriate for which the proof outline given in \secref{sec:sec of construction} holds.  We need a distribution where after all of the possible equality queries, a large number of blocks still have super-logarithmic entropy.

@@

\begin{theorem}
Let $\mathcal{W}$ be a family of $(q, \omega(\log n),  \beta)$-unguessable distributions over $\zo^{n\times \ell}$.  Furthermore, let $C$ be a $(\neigh_t, \epsilon_{code})$-code.  Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\zo^{n\times \ell}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon, s_{sec})$ with error $\epsilon_{code} + \ell/2^n$ and resulting entropy $\tilde{m} = \log |C| - \beta - o(n)$.
\end{theorem}

\subsection{Characterizing unguessable block distributions}
\bnote{This section needs to be finished.  The point is to try and give an idea what the above definition means.  What type of distributions fulfill that definition.}
This type of source seems to be inherently adaptive and is difficult to formulate in a clean information-theoretic notion.  However, we can show necessary and sufficient types of sources for a guessable block distribution.  We begin by defining the entropy jump of a block source which will appear in our characterization.

\begin{definition}
Let $W = W_1,..., W_k$ be a source under ordering $i_1,..., i_k$.  The \emph{entropy jump} of a block $i_j$ is $J(i_j) = \Hav(W_{i_j} | W_{i_1},..., W_{i_{j-1}})$.
\end{definition}

\begin{claim}
Let $W$ be a $(q, \alpha, \ell)$-unguessable block distribution.  Then for all orderings $i_1, ...., i_k$ there is some $j\leq k-\ell$ such that $J(i_j)> \log q + \alpha$.
\end{claim}
\begin{proof}
Suppose not, for convenience assume the ordering that violates this condition is $1,..., k$.  We describe a distribution $W$ where $\forall 1\leq j\leq k-\ell$, $J(j)\leq \log q +\alpha$. Define $W$ as follows $W_1 = c_1,...., W_{j-1} = c_{j-1}$ are constants.
\end{proof}
\bnote{keep working}

>>>>

We now describe a set of high entropy sources appropriate for which the proof outline given in \secref{sec:sec of construction} holds.  We need a distribution where after $q$-equality queries, a large number of blocks still have super-logarithmic entropy.

@@

\begin{theorem}
Let $\mathcal{W}$ be a family of $(q, \omega(\log n),  \beta)$-unguessable distributions over $\zo^{n\times \ell}$ for any $q = \poly(n)$.  Furthermore, let $C$ be a $(\neigh_t, \epsilon_{code})$-code.  Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\zo^{n\times \ell}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon, s_{sec})$ with error $\epsilon_{code} + \ell/2^n$ and resulting entropy $\tilde{m} = \log |C| - \beta - o(n)$.
\end{theorem}

\subsection{Characterizing unguessable block distributions}

\defref{def:block guessable} is an inherently adaptive definition and thus a little unwieldy for a distribution.  In this section, we provide a limited characterization of sources satisfy \defref{def:block guessable} and distributions that are learnable by equality queries.

The majority of the difficulty in characterizing the definition is that different blocks may be dependent so a equality query on block $i$ may shape the distribution of block $j$.  Thus, we begin with the case of independent blocks.

\begin{claim}
\label{cl:independent high ent}
Let $W = W_1,..., W_\ell$ be a source where blocks are independent.  Let $\mathcal{I}$ be the set of blocks such that $\Hoo(W_i ) =\alpha $.  Then $W$ is a $(q, \alpha - \log (q+1), \ell - |\mathcal{I}|)$-block unguessable distribution.  In particular, when $\alpha = \omega(\log n)$ and $q = \poly(n)$, then $W$ is a $(q, \omega(\log n), \ell - |\mathcal{I}|)$-block unguessable distribution.
\end{claim}
\begin{proof}
We ignore the blocks outside of $\mathcal{I}$ as queries on these blocks do not change the distribution of $W_i$ where $i\in \mathcal{I}$.  It suffices to show that for all $i\in \mathcal{I}, \Hav(W_i) = \alpha -\log q$.  As argued in the proof of \lemref{lem:blocks unguessable after queries}, we can consider the sequence of queries without duplicates~(as duplicate queries provide no additional information and do not increase the number of possible response strings).  Then there are at most $q+1$ possible response strings~(all strings of Hamming weight at most $1$).  Then by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08} we have that 
\[
\Hav(W_i | View(A^{\mathcal{O}_{W}(\cdot, \cdot)})) \geq \Hav(W_i | View(A^{\mathcal{O}_{W}(i, \cdot)})) \geq \Hoo(W_i) -\log (q+1).
\]
\end{proof}
In their work on computational fuzzy extractors, Fuller, Meng, and Reyzin~\cite{fuller2013computational} consider block-fixing sources, where each block is either uniform or a fixed symbol~(block fixing sources were introduced by Kamp and Zuckerman~\cite{KZ07}).  This is a subset of the distributions in \clref{cl:independent high ent}.

We now consider more complicated~(realistic) distributions where blocks are not independent.  We begin with distributions that are block unguessable.

\begin{claim}
\label{cl:each block from single seed}
Let $e =\omega(\log n)$ and let $f:\zo^e \rightarrow \zo^{n\times \ell}$ be a function.  Furthermore, let $f_i$ denote the restriction of $f$'s output to the bits $[i\times n,..., i\times n+n-1]$.  If for all $i, f_i$ is injective then $W = f(U_e)$ is a $( q, e - \log (q+1), 0)$-block unguessable distribution.
\end{claim}
\begin{proof}
Since $f$ is injective on each block, $\Hav(W_i | View(A^{\mathcal{O}_{W}(\cdot, \cdot)})) = \Hav(U_e | View(A^{\mathcal{O}_{W}(\cdot, \cdot)}))$.  Consider a query $q_j$ on block $i$, there are two possibilities either $q_j$ is not in the image of $f_i$ on $q_j$ can be considered a query on the preimage $f_i^{-1}(q_j)$.  Thus, a query eliminates at most a single value of $U_e$, this holds for all blocks $i$.  Then similarly to the proof of \clref{cl:independent high ent}, we can eliminate queries which correspond to the same value of $U_e$.  Then the possible responses are strings with Hamming weight at most $1$ and by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08} we have for all $i$, $\Hav(W_i | View(A^{\mathcal{O}_{W}(\cdot, \cdot)})) \geq \Hoo(W_i) -\log (q+1)$.
\end{proof}

Note the total entropy of a source in \clref{cl:each block from single seed} is $e$, so this is a family of distributions with total entropy $\omega(\log n)$ where \consref{cons:first construction} is secure.  This claims rests on there being no easy ``entry'' point to the distribution.  This is not always the case.  Indeed it is possible for some blocks to have very high entropy but lose all of it after equality queries.

\begin{claim}
Let $p = (\poly(n))$, let $X = U_{\log p\times \ell}$ be a distribution and let $f_1,..., f_{\ell}$ be injective functions where $f_i:\zo^{i\times \log p}\rightarrow \zo^n$.\footnote{Here we assume that $n\ge \ell \times \log p$, that is the source has a small number of blocks.}  Then define the distribution $W_1 = f_1(U_{1,...,\ell}), W_2 = f_2(U_{1,..., 2\ell}),...., W_\ell = f_\ell(U)$.  There is an adversary making $2^e\times \ell = \poly(n)$ queries such that $\Hav(W | View(A^{\mathcal{O}_W(\cdot, \cdot)})) = 0$.
\end{claim}
\begin{proof}
We present an adversary $A$~(running in polynomial time) that completely determines the value $x$.  $A$ computes $y_1^1 = f_1(x_1^1),..., y_1^p = f(x_1^p)$.  Then $A$ queries on $y_1,..., y_p$ exactly one answer returns $1$.  Let this value be $y_1^*$ and its preimage $x_1^*$.  Then $A$ computes $y_2^1 = f_2(x_1^*,x_2^1), ..., y_2^p= f_2(x_1^*, x_2^p)$ and queries $y_2^1,..., y_2^p$.  Again, exactly one of these queries returns $1$.  This process is repeated until all of $x$ is recovered.  The total space complexity of this algorithm can be reduced to a single query~(by computing $y$ as necessary) as its total time is $O(p\times \ell)$.  Once $x$ has been recovered then $\Hav(W | View(A^{\mathcal{O}_W(\cdot, \cdot)})) = 0$.
\end{proof}

The previous example relied on an adversaries ability to completely determine a block from the previous blocks.  We formalize this notion next.  We defining the entropy jump of a block source as the remaining entropy when other blocks are known:

\begin{definition}
Let $W = W_1,..., W_\ell$ be a source under ordering $i_1,..., i_\ell$.  The \emph{entropy jump} of a block $i_j$ is $J(i_j) = \Hav(W_{i_j} | W_{i_1},..., W_{i_{j-1}})$.
\end{definition}

We now show that there must be a super-logarithmic jump early enough.

\begin{claim}
Let $W$ be a distribution and let $q$ be a parameter, if there exists an ordering $i_1,..., i_\ell$ such that for all $j\le \ell-\beta +1$, $J(i_j) = \log q /\ell$, then $W$ is not $(q, 0, \beta)$-unguessable.
\end{claim}

%\begin{claim}
%Let $W$ be a $(q, \alpha, \ell)$-unguessable block distribution.  Then for all orderings $i_1, ...., i_k$ there is some $j\leq k-\ell$ such that $J(i_j)> \log q + \alpha$.
%\end{claim}
\bnote{I instead of min-entropy here we want support size.  Are we okay with that?  Not sure how this adapts to average min-entropy.}
\begin{proof}
For convenience relabel the ordering that violates the condition as $1,..., \ell$.  We describe an unbounded adversary that determines $W_1,..., W_{\ell-\beta+1}$.  As before $A$ queries the $q /\ell$ possible values for $W_1$ and determines $W_1$.  Then $A$ queries the $q/\ell$ possible values for $W_2 | W_1$.  This process is repeated until $W_{\ell-\beta+1}$ is learned.  Note the optimum ordering for the adversary can be encoded nonuniformly but it may take an unbounded amount of time/space to construct $W_i | W_1,.., W_{i-1}$.
\end{proof}
